Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2024-05-08 paper/paper.tex
Fix affiliation (add more emails if you want)

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}
\short{preCICE on Nix: A case study}
\author{
Max Hausch\autref{1+},
Simon Hauser\autref{2+},
Benjamin Uekermann\autref{3}}

\institute{
\autlabel{1} \email{st175425@stud.uni-stuttgart.de}\\
\autlabel{2} \email{st148883@stud.uni-stuttgart.de}\\
\autlabel{3} \email{Benjamin.Uekermann@ipvs.uni-stuttgart.de}\\
\autlabel{+} These authors contributed equally to this work.}

>>>>

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}
\short{preCICE on Nix: A case study}
\author{
Max Hausch\autref{1}\autref{*},
Simon Hauser\autref{1}\autref{*},
Benjamin Uekermann\autref{1}}

\institute{
\autlabel{1} Institute for Parallel and Distributed Systems\\ University of Stuttgart\\ \email{benjamin.uekermann@ipvs.uni-stuttgart.de}\\
%\autlabel{1} \email{st175425@stud.uni-stuttgart.de}\\
%\autlabel{2} \email{st148883@stud.uni-stuttgart.de}\\
\autlabel{*} These authors contributed equally to this work.}
